Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-08-07 submission/manuscript.Rmd
P2 Ada suggestions discussion

Although SCFAs have been shown to be anti-tumorigenic, most of these studies have been performed in model systems [@test_OKeefe2016; @Encarnao2018]. Additionally, many of the *in vivo* studies investigate proxies such as fiber supplementation rather than SCFAs directly [@Holscher2017]. Although it is well known that breakdown products from gut bacteria results in SCFA production, fiber effects on tumorigenesis may be through other mechanisms in these *in vivo* model systems. In addition to using fiber supplementation as a proxy for SCFA treatment, observations on the benefit of SCFAs in preventing tumorigenesis has been mixed. In previous case/control studies lower SCFA concentrations between patients with carcinomas and those without carcinomas was observed [@Ohigashi2013]. Yet, this is in contrast to multiple randomized-controlled trials that have found no difference between patients who do and do not get fiber supplementation to try and prevent tumor recurrence [@Schatzkin2000; @Yao2017]. This could be because fiber has other actions in humans besides providing an energy source for bacteria to breakdown to make SCFAs. It could also be due to the fact that SCFA concentrations and responses to fiber can vary quite a bit between healthy individuals [@scfa_measures_venkataraman2016]. This information taken together with our observations would suggest that either individuals who do not respond to fiber supplementation would need to acquire these bacteria to achieve a benefit or that SCFAs provide little to no benefit as an anti-tumorigenic compound in colorectal cancer.

>>>>

Although SCFAs have been shown to be anti-tumorigenic, most of these studies have been performed in model systems [@test_OKeefe2016; @Encarnao2018]. Many of the *in vivo* studies use proxies such as fiber supplementation rather than SCFAs directly [@Holscher2017]. Although it is well known that breakdown products from gut bacteria results in SCFA production, fiber effects on tumorigenesis may be through other mechanisms in these *in vivo* model systems. Additionally, the observations in humans on the benefit of SCFAs in preventing tumorigenesis have been mixed. In previous case/control studies lower SCFA concentrations were observed in patients with carcinomas versus those without carcinomas [@Ohigashi2013]. Yet, this is in contrast to multiple randomized-controlled trials that have found no difference in tumor recurrence between patients who do and do not get fiber supplementation [@Schatzkin2000; @Yao2017]. In contrast to the *in vivo* model findings, the observations made in these randomized-controlled trials would suggest that SCFAs do not prevent or slow tumorigenesis. One reason for these results is that SCFA concentrations and responses to fiber vary quite a bit between healthy individuals [@scfa_measures_venkataraman2016]. This information taken together with our observations would suggest that either individuals who do not respond to fiber supplementation would need to acquire these bacteria to achieve a benefit or that SCFAs provide little to no benefit as an anti-tumorigenic compound in colorectal cancer.

### 2018-08-07 submission/manuscript.tex
P2 Ada suggestions discussion

Although SCFAs have been shown to be anti-tumorigenic, most of these
studies have been performed in model systems (16, 17). Additionally,
many of the \emph{in vivo} studies investigate proxies such as fiber
supplementation rather than SCFAs directly (14). Although it is well
known that breakdown products from gut bacteria results in SCFA
production, fiber effects on tumorigenesis may be through other
mechanisms in these \emph{in vivo} model systems. In addition to using
fiber supplementation as a proxy for SCFA treatment, observations on the
benefit of SCFAs in preventing tumorigenesis has been mixed. In previous
case/control studies lower SCFA concentrations between patients with
carcinomas and those without carcinomas was observed (19). Yet, this is
in contrast to multiple randomized-controlled trials that have found no
difference between patients who do and do not get fiber supplementation
to try and prevent tumor recurrence (20, 23). This could be because
fiber has other actions in humans besides providing an energy source for
bacteria to breakdown to make SCFAs. It could also be due to the fact
that SCFA concentrations and responses to fiber can vary quite a bit
between healthy individuals (24). This information taken together with
our observations would suggest that either individuals who do not
respond to fiber supplementation would need to acquire these bacteria to
achieve a benefit or that SCFAs provide little to no benefit as an
anti-tumorigenic compound in colorectal cancer.

>>>>

Although SCFAs have been shown to be anti-tumorigenic, most of these
studies have been performed in model systems (16, 17). Many of the
\emph{in vivo} studies use proxies such as fiber supplementation rather
than SCFAs directly (14). Although it is well known that breakdown
products from gut bacteria results in SCFA production, fiber effects on
tumorigenesis may be through other mechanisms in these \emph{in vivo}
model systems. Additionally, the observations in humans on the benefit
of SCFAs in preventing tumorigenesis have been mixed. In previous
case/control studies lower SCFA concentrations were observed in patients
with carcinomas versus those without carcinomas (19). Yet, this is in
contrast to multiple randomized-controlled trials that have found no
difference in tumor recurrence between patients who do and do not get
fiber supplementation (20, 23). In contrast to the \emph{in vivo} model
findings, the observations made in these randomized-controlled trials
would suggest that SCFAs do not prevent or slow tumorigenesis. One
reason for these results is that SCFA concentrations and responses to
fiber vary quite a bit between healthy individuals (24). This
information taken together with our observations would suggest that
either individuals who do not respond to fiber supplementation would
need to acquire these bacteria to achieve a benefit or that SCFAs
provide little to no benefit as an anti-tumorigenic compound in
colorectal cancer.
